decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-04 README.Rmd
Update figure

---
title: "decompr: trade flow decomposition for Global Value Chain analysis"
author: "Bastiaan Quast and Victor Kümmritz"
date: "Wednesday, November 26, 2014"
output: md_document
bibliography: bibliography.bib
---

@@

Abstract
===============
The R package **decompr** implements algorithms for the analysis of Global Value Chains.
Two methods for gross export flow decomposition using Inter-Country Input-Output tables are provided.
The first method is the **Wang-Wei-Zhu** [-@wang2014quantifying] algorithm which splits bilateral gross exports into 16 value added components.
These components can broadly be divided into domestic and foreign value added.
The second method concerns a **source decomposition** algorithm.
This derives the value added origin of a country-industry’s exports by source country and source industry,
by applying the basic Leontief insight to gross trade data.
This article summarises the methodology of the algorithms and describes the format of the input and output data.

>>>>

---
title: "decompr: trade flow decomposition for Global Value Chain analysis"
author: "Bastiaan Quast and Victor K??mmritz"
date: "Wednesday, November 26, 2014"
output: md_document
bibliography: bibliography.bib
---

@@

Abstract
===============
The R package **decompr** implements algorithms for the analysis of Global Value Chains.
Two methods for gross export flow decomposition using Inter-Country Input-Output tables are provided.
The first method is the **Wang-Wei-Zhu** [-@wang2014quantifying] algorithm which splits bilateral gross exports into 16 value added components.
These components can broadly be divided into domestic and foreign value added.
The second method concerns a **source decomposition** algorithm.
This derives the value added origin of a country-industry???s exports by source country and source industry,
by applying the basic Leontief insight to gross trade data.
This article summarises the methodology of the algorithms and describes the format of the input and output data.
